\row{}{%
    \cvtitle{Denis Frezzato}\newline
    \jobdescription{full stack JavaScript developer}\newline
    \tag{residence} Milano, via Domenico Berra 16/19, 20132 (MI)\newline
    \tag{\mdPhone} \href{tel:00393477220550}{+393477220550}\newline
    \tag{\mdMail} \href{mailto:denis.frezzato@tutanota.com}{denis.frezzato@tutanota.com}\newline
    \tag{\faGithub} \href{https://github.com/DenisFrezzato}{DenisFrezzato}%
}

\vmargin
\row{}{\sectiontitle{Work experience}}

\row{\tag{from May 2019}}{%
    \textbf{Full stack developer} at Penta\newline
    Working on a digital bank for SMEs. Development of the frontend using React. Development of the backend using Node.js, PostgreSQL, Redis. Began migration to TypeScript and introduced functional programming paradigms.
}

\row{\tag{from December 2019\break to May 2019}}{%
    \textbf{Front end developer} at Beesy\newline
    Working on an italian invoicing solution. Development of the web application with React. Began migration to TypeScript and introduced functional programming paradigms.
}

\row{\tag{from July 2017\break to December 2019}}{%
    \textbf{Full stack developer} at Trovami\newline
    Development of a social directory, the frontend using React, the backend using a microservice architecture based on Node.js, MongoDB, Elasticsearch, RabbitMQ, Redis. Development of RESTful APIs based on Node.js\newline and PostgreSQL. Development of web application using React e React Native. Maintenance works on Drupal and WordPress websites.%
}

\row{\tag{from December 2015\break to July 2017}}{%
    \textbf{Full stack developer} at I-Glue\newline
    Development of Drupal and WordPress websites (custom themes and modules). Development of hybrid applications using Cordova, Ionic and Angular. Development of RESTful API based on Node.js, MongoDB and MySQL. Development of web application based on Zend Framework 2. Development of SPA using React. Development of a web application using a microservice architecture based on Node.js, MongoDB, Elasticsearch, RabbitMQ, Redis.%
}

\row{\tag{from February 2015\break to December 2015}}{%
    \textbf{Full stack developer} freelance\newline
    Development of Drupal and WordPress websites (custom themes and modules). Development of web application based on Zend Framework 2.%
}

\row{\tag{from June 2014\break to February 2015}}{%
    \textbf{Front end developer} at Alchimedia\newline
    Front end development of theme-based websites.%
}

\row{\tag{from October 2013\break to June 2014}}{%
    \textbf{Graphic design, web design e web developer} at visualmade\newline
    Graphic design of printed products and websites. Static websites development.%
}

\newpage
\row{}{\sectiontitle{Education}}

\row{\tag{July 2013}}{%
    \textbf{Bachelor of Science: Communication Design} - Polytechnic University of Milan, vote 97/110.%
}

\row{\tag{July 2008}}{%
    \textbf{High school: Information technology} at I.T.I.S. G. Segato in Belluno.%
}

\vmargin
\row{}{\sectiontitle{Languages}}

\row{}{%
    \textbf{Italian}\newline
    Native speaker.%
}

\row{}{%
    \textbf{English}\newline
    Good working knowledge in spoken and written English.%
}

\vmargin
\row{}{\sectiontitle{Technical skills}}

\row{}{%
    \textbf{Operative systems}\newline
    Linux, Windows, Mac OSX.%
}

\row{}{%
    \textbf{Programming languages}\newline
    Excellent working knowledge in HTML5, CSS3 and SASS, JavaScript (ES5, ES6, ES7, Node.js) and TypeScript.%
}

\row{}{%
    \textbf{Libraries, frameworks and CMS}\newline
    Excellent working knowledge in React and React Native, Redux, ExpressJS SenecaJS, hapi and Zend Framework 2. Excellent working knowledge in Drupal and WordPress. Basic working knowledge in AngularJS and Ionic.%
}

\row{}{%
    \textbf{Databases}\newline
    Good working gnowledge in PostgreSQL, MySQL, MongoDB and Elasticsearch. Basic working knowledge in Redis.%
}

\row{}{%
    \textbf{Tools}\newline
    Excellent working knowledge in Git and Docker.%
}

\vmargin
\row{}{\sectiontitle{Hobbies and personal interests}}

\row{}{%
    Technologies, music, reading, photography, design, climbing.\newline
    I often participate at local MeetUps regarding information technologies.%
}